---
title: "Stock Report"
date: 2021-04-10
output: html_document
params:
  STOCK_NAME: "LHBA"
  PRICE_FILE: "data/Bank_Price.csv"
  VOL_FILE: "data/Bank_Volume.csv"
---

# Volatility Report for **`r params$STOCK_NAME`** during 2014-2019
  
```{r setup, include=FALSE}
  library(tidyverse)
  library(lubridate)
  library(rugarch)
  library(moments)
  source("main.R")
  library(cowplot)
  library(tseries)
  knitr::opts_chunk$set(fig.width = 6, fig.asp = 0.3) 
  
  # Possible Alternative Stocks:
  # BBLT
  # TMBT
  # TFBT
  # SBBT
```

Descriptive Summary and Plot
----------------------------------------------------------
  
```{r, include = FALSE}
  cleaned_df <- Clean_df(params$STOCK_NAME, params$PRICE_FILE,
                         params$VOL_FILE)
  result_GARCH <- Run_model(cleaned_df, "garch")
  result_GJR <- Run_model(cleaned_df, "gjr")
```
  
  
```{r, echo = FALSE, message = FALSE, warning = FALSE}
  plot1 <- ggplot(cleaned_df, aes(Date, log_ret)) + geom_line()
  plot2 <- ggplot(cleaned_df, aes(log_ret)) + geom_histogram()
  
  plot_grid(plot1, plot2, labels = "AUTO")
```
  
```{r, include = FALSE}
  minimum <- min(cleaned_df$log_ret)
  p_25 <- quantile(cleaned_df$log_ret, 0.25)[[1]]
  p_50 <- quantile(cleaned_df$log_ret, 0.50)[[1]]
  p_75 <- quantile(cleaned_df$log_ret, 0.75)[[1]]
  maximum <- max(cleaned_df$log_ret)
  
  skewness <- skewness(cleaned_df$log_ret)
  kurtosis <- kurtosis(cleaned_df$log_ret)
  jb <- jarque.bera.test(cleaned_df$log_ret)
  jb_stat <- jb$statistic
  jb_p <- jb$p.value
  
  summary <- tribble(
  ~Minimum, ~`25% Percentile`, ~Median, ~`75% Percentile`, ~Maximum,
  #-----|-----|-----|-----|-----
  minimum, p_25, p_50, p_75, maximum
  )
  
  advanced <- tribble(
  ~Skewness, ~Kurtosis, ~JarqueBeraStat, ~JarqueBeraPVal,
  #-----|-----|-----|-----
  skewness, kurtosis, jb_stat, jb_p
  )
```

```{r, echo = FALSE}
  knitr::kable(
  summary, 
  caption = "Basic Statistics"
)
```

```{r, echo = FALSE}
  knitr::kable(
  advanced, 
  caption = "Advanced Statistics"
)
```

Model Result
-----------------------------------------------------
```{r, echo = FALSE}
  knitr::kable(
  result_GARCH[["Goodness"]], 
  caption = "GARCH Estimation Result"
)
```
### Interpretation:  
1. Average return is `r result_GARCH[["Coef"]][["mu"]]`.  
1. If volatility in the previous period increases by 1% (squared), the current period volatility would change by `r result_GARCH[["Coef"]][["beta1"]]`% (squared). 
1. If deviation from mean increases by 1%, the volatility would change by `r result_GARCH[["Coef"]][["alpha1"]]`%.  
 


```{r, echo = FALSE}
  knitr::kable(
  result_GJR[["Goodness"]], 
  caption = "GJR-GARCH Estimation Result"
)
```
### Interpretation:  
1. Average return is `r result_GJR[["Coef"]][["mu"]]`.  
1. If volatility in the previous period increases by 1% (squared), the current period volatility would change by `r result_GJR[["Coef"]][["beta1"]]`% (squared).  
1. If deviation from mean increases by 1% and the deviation is positive, the volatility would change by `r result_GJR[["Coef"]][["alpha1"]]`%.  
1. If deviation from mean increases by 1% and the deviation is negative, the volatility would change by `r result_GJR[["Coef"]][["alpha1"]] + result_GJR[["Coef"]][["gamma1"]]`%.  


